---
title: "SoS Reinforcement - Supplemental report"
date: "`r Sys.Date()`"
output:
  github_document:
    toc: yes
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

source("./wrangle_sos.R")
source("./analysis_sos.R")
source("./supplemental_analysis_sos.R")

```

## Fixed effects models with alternate coding of stages

In the models below we code stage 4 as the midpoint of the interview (all non critical stages) instead of point 3. These models do not change our interpretation of our int ital results.

### Main effect model

```{r}
summary(info_model_M4)
```

### Interaction effect model

```{r}
summary(info_model_M4_int)
```

### Model comparison 

```{r}
comp_model_anova
```

## Predicting perceived interview quality by disclosed details

While the relationship between perceived interviewer quality and information disclosures differed across the conditions, perceived interview quality did not.

### Main effect model

```{r}
summary(expl_model_5)
```

### Interaction effect model

```{r}
summary(expl_model_6)
```

### Model comparison

```{r}
comp_expl_model_anova_3
```

## Assessing Training effects

### Main effect model
```{r}
summary(training_model_1)
```

### Interaction effect model
```{r}
summary(training_model_2)
```

### Model comparison
```{r}
training_anova
```

## Comparing interviewers

```{r}
interviewer_desc_2
```

### M vs. P
```{r}
t_interviewer_MP
```

### M vs. K
```{r}
t_interviewer_MK
```

### P vs. K
```{r}
t_interviewer_PK
```

## Duration of interview

```{r}
duration_desc
```

### Main effect model

```{r}
summary(dur_model_1)
```

### Interaction effect model

```{r}
summary(dur_model_2)
```

### Model comparison

```{r}
dur_model_anova
```

